A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-05 paper.tex
comment

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations and believe this framework
is also applicable to other cast representations.
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and hypothetically consume less memory than coercions
in normal forms.

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: I think readers should be able to trace back history by following the pointers in the 
intro section. I don't know whether my thought is correct. I would rather not giving misleading
pointers. I also don't know how far should a pointer chases back. Readers can be directed to recently
works which will eventually lead them back to the earliest possible paper. But wouldn't it be
great if the author of a new paper shows reader all the milestones? After all we already know 
pointer dereferencing is expensive.}

>>>>

\begin{document}
%
\title{A Framework for Equivalence of Cast Calculi and a new Cast Representation}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Kuang-Chen Lu\inst{1} \and
Jeremy G. Siek\inst{2} \and
Andre Kuhlenschmidt\inst{2}
}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Brown University, Providence RI 02912, USA \and
Indiana University, Bloomington IN 47405, USA}
% \institute{Princeton University, Princeton NJ 08544, USA \and
% Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
% \email{lncs@springer.com}\\
% \url{http://www.springer.com/gp/computer-science/lncs} \and
% ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
% \email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Gradual typing aims at combining dynamic typing and static typing in one 
language to provide the advantages of both typing disciplines. Implementing 
gradual typing with reasonable overhead, however, is not trivial. Casts might 
accumulate in higher-order values and continuations, thus change the overall 
space complexity. Several space-efficient cast representations have been 
proposed, notably coercions in normal forms and threesomes. But they are
presented in different dynamic semantics, which make it difficult to compare
the key differences between the cast representations. We present a abstrat
data type, namely Cast ADT, that captures interface functions a cast representations
typically includes, and an abstract machine parameterized over Cast ADTs.
The Cast ADT brings another benefit: space-efficient cast representations 
shall be proved not changing the 
overall behavior of language implementations except saving space.
With our generic abstract machine, these proofs can be done by proving properties
of a specific Cast ADT, which is simpler than going through a bisimulation proof 
between a space-efficient dynamic semantics and the definitional dynamic semantics.
We have successfully applied our new approach of proving the correctness of cast 
representations to several known cast representations and believe this framework
is also applicable to other cast representations.
\todo[inline]{JS: cite which other cast representations}
We also present a new cast representation, hypercoercions, that is more friendly
to mechanized meta-theory and hypothetically consume less memory than coercions
in normal forms.

@@

\todo[inline]{KC: Cite "Contracts for higher-order functions" for the proxy-based approach maybe?}
\todo[inline]{JS: That paper doesn't exactly fit into what you're talking about in the above
sentence. It might be appopriate to cite it elsewhere in the paper. Also,
there are earlier papers about coercive subtyping (Computing with coercions by Breazu-Tannen et al)
that use a proxy-based approach. The contracts paper may be the first to propose blame tracking.}
\todo[inline]{KC: I think readers should be able to trace back history by following the pointers in the 
intro section. I don't know whether my thought is correct. I would rather not giving misleading
pointers. I also don't know how far should a pointer chases back. Readers can be directed to recently
works which will eventually lead them back to the earliest possible paper. But wouldn't it be
great if the author of a new paper shows reader all the milestones? After all we already know 
pointer dereferencing is expensive.}
\todo[inline]{JS: Yes, citing the original paper for each idea is great.
  I'm just saying 1) cite the correct paper for each idea and 2)
  talk about the various ideas in an organized way with respect
  to your sentence and paragraph structure.}
